\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{scrextend}

%\usepackage{showframe} % debugging use only

\geometry{
  letterpaper,
  left = 0.5in,
  right = 0.5in,
  top = 0.6in,
  bottom = 0.6in
}

\hypersetup{
  colorlinks = true, 
  linkcolor = blue, 
  urlcolor  = blue,
  citecolor = blue, 
  anchorcolor = blue
}

%   CUSTOM STYLES  %
\thispagestyle{empty} % remove page number
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%   MACROS  %
\newcommand{\sectionStart}{
  \begin{itemize}[label={},leftmargin=0in]
}
\newcommand{\sectionEnd}{
  \end{itemize}
}
\newcommand{\summaryText}[1]{
  \item
  \begin{addmargin}[7pt]{0pt}
    {#1}
  \end{addmargin}
}
\newcommand{\companySummaryText}[1]{
  \begin{addmargin}[15cm]{3cm}
  {#1 \vspace{-1.8pt}}
  \end{addmargin}\vspace{5pt}
}
\newcommand{\educationItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r@{}}
    {#1}  & {#2}\\
  \end{tabular*}
  \vspace{-5pt}
}
\newcommand{\skillItem}[2]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{}l@{}}
    {\textbf{#1}: } & {#2}
  \end{tabular*}\vspace{-17pt}
}
\newcommand{\jobHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{\textbf{#1}} & #2 \\
    \textit{\small#3}
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\projectHeading}[4]{
  \vspace{-1pt}
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r@{}}
    \normalsize{{\href{#1}{#2}} \textbf{#3}} & #4 \\
  \end{tabular*}\vspace{-5pt}
}
\newcommand{\listStart}{\begin{itemize}}
\newcommand{\listEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\bulletItem}[1]{
  \item
  \small{
    {#1 \vspace{-1.8pt}}
  }
}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{
      \textbf{\href{https://naighes.github.io/}{\color{black}{\LARGE {\underline{Nicola Baldi}}}}}
    }
    \vspace{5pt}\\
    \centerline{
      \href{mailto:nic.baldi@gmail.com}{\underline{nic.baldi@gmail.com}} $\mid$
      +39 (348) 912-8888 $\mid$
      Github : \href{https://github.com/naighes}{\underline{naighes}} $\mid$
      LinkedIn : \href{https://www.linkedin.com/in/nicolabaldi}{\underline{nicolabaldi}} $\mid$
      Slideshare : \href{https://www.slideshare.net/Naighes}{\underline{Naighes}}
    }
  \end{tabular*}
  \vspace{-5pt}

\section{Summary}
\sectionStart
  \summaryText
  {Manager, Speaker, hands-on Architect driving the vision and the technology strategy of companies to make them more effective. Open-minded, critical thinker and relentless learner never afraid of getting out of the comfort zone. Software craftsmanship, Open Source and DevOps advocate. Performance-addicted, passionate about languages and distributed/highly scalable architectures.}
\sectionEnd

\section{Technical Skills}
\sectionStart
  \skillItem
    {Languages}
    {JavaScript, Typescript, C\#, C, OCaml, Go, Swift, Kotlin}
  \skillItem
    {Tools}
    {Git, Bash, Powershell, Docker, Kubernetes, Terraform, \LaTeX\ }
  \skillItem
    {Databases}
    {Microsoft SQL Server, Cassandra, DynamoDB, MongoDB, Redis}
  \skillItem
    {Methodologies}
    {Agile Methodologies (mainly XP), CI and CD, TDD, IaaC}
  \vspace{3pt}
\sectionEnd
  
%   EXPERIENCE   %
\section{Experience}
\sectionStart
  \jobHeading
    {Senior Software Architect and Developer}
    {Nov 2016 - Present}
    {YOOX NET-A-PORTER Group}
  \sectionStart
    \summaryText
    {The world's leading online luxury fashion retailer, with 4 multi-brand online stores and 40 online flagship stores, YOOX NET-A-PORTER GROUP has around 500 developers out of 5000 employees, offices and operations in the USA, Europe, Japan, China and Hong Kong and delivers to more than 180 countries and 3 million customers around the world.}
  \sectionEnd
  \listStart
    \bulletItem
    {Mentored the yoox.com area towards the adoption of a cloud-native approach.}
    \bulletItem
    {Led the migration of yoox.com application ecosystem from on-premises to hybrid cloud to public cloud (AWS).}
    \bulletItem
    {Drove the adoption of containers with Docker and Kubernetes moving from VMs to AWS ECS and AWS EKS resulting in a significant reduction in time to market.}
    \bulletItem
    {Led the design and the implementation of fully automated ``on demand" environments by defining the software and infrastructure development life cycles, detailing workflow, tools and practices: sizing, usage, provisioning, configuration management, versioning, testing, development, deployment, release management.}
    \bulletItem
    {Defined the strategy for observability: access/error/audit logging, monitoring, alerting and distributed tracing.}
    \bulletItem
    {Held training sessions and created internal communities.}
  \listEnd
  \sectionStart
    \skillItem
    {Key technologies}
    {Go, Typescript, Terraform, Docker, K8S, Jaeger, Prometheus, React/Redux, C\#, GraphQL}
  \sectionEnd
\sectionEnd

\sectionStart
  \jobHeading
    {Head of Back-end Platform Architecture}
    {Feb 2014 - November 2016}
    {YOOX Group}
  \sectionStart
    \summaryText
    {YOOX Group, a global Internet retailing partner for leading fashion & design brands. YOOX has established itself amongst the market leaders with the multi-brand stores yoox.com, thecorner.com and shoescribe.com, as well as with numerous mono-brand online stores such as Diesel, Armani, Bottega Veneta and Dolce & Gabbana.}
  \sectionEnd
  \listStart
    \bulletItem
    {Provided guidance to the fulfillment department along the journey for the shift to the omni-channel capabilities.}
    \bulletItem
    {Defined group-wide and multi-tenant API implementation guidelines to improve platform stability, maintainability and make its evolution easier (ReST architectural style with particular emphasis on HATEOAS and in complementarity with GraphQL for a safer service-to-service communication).}
    \bulletItem
    {Complete rewrite of the Order Management System to adopt an event-driven architecture guaranteeing a seamless integration with the new Warehouse Management System and London based Net-A-Porter logistic hubs.}
    \bulletItem
    {Increased conversion rate with a minimum cost impact by means of AWS Lambda serverless solutions.}
    \bulletItem
    {Overhauled the catalog generation process reducing processing time by 50\%.}
    \bulletItem
    {Defined the engineering department interview assessment criteria and tests in collaboration with the people team.}
  \listEnd
  \sectionStart
    \skillItem
    {Key technologies}
    {RabbitMQ, Docker, Apache Solr, SQL Server, MongoDB, AWS DynamoDB, AWS Lambda}
  \sectionEnd
\sectionEnd

\sectionStart
  \jobHeading
    {Software Developers Manager}
    {Jun 2013 - Feb 2014}
    {YOOX Group}
\sectionEnd

\sectionStart
  \jobHeading
    {Software Developer}
    {Jan 2011 - May 2013}
    {LUISAVIAROMA}
\sectionEnd

\sectionStart
  \jobHeading
    {Software Developer}
    {May 2007 - Jan 2011}
    {ATOdesign s.r.l.}
\sectionEnd

\section{Education}
\sectionStart
  \educationItem
    {BD, Faculty of Computer Science (Università di Pisa)} 
    {ongoing} 
  \educationItem
    {ITIS E. Fermi Lucca}{}
\sectionEnd

\end{document}
